State and Input Dependent Disturbances in Min-Max Model Predictive Control

### 2015-10-23 draft.tex
Minor changes.
what happened

[ticket: X]

In this section we discuss how multi-parametric quadratic programs (mpQP) can be solved efficiently with an active-set 
solver (see e.g.~\cite{Fletcher:1987}).

@@

It can be shown (see~\cite{Schaich:NMPC:2015}) that the solution of~\eqref{app:kkt:conditions} has the structure

@@

(see e.g.~\cite{Bryson:1975}, this yields

>>>>

In this section we discuss how multi-parametric quadratic programs (mpQP, see e.g.~\cite{Tondel:2003,Bemporad:2002} 
for elaborate discussions) can be solved efficiently with an active-set solver (see e.g.~\cite{Fletcher:1987}).

@@

which we can solve explicitly.

@@

(see e.g.~\cite{Bryson:1975}), this yields
